Effort and Delay Discounting in a Foraging Environment

### 2019-05-08 Cost2/Cost2_prereg_remake.Rmd
cost 2 script updated to be more readable

``` {r 16.2.1. Overall Proportion/Earnings,fig.align="center",fig.width=10,fig.height=4, echo=FALSE}  
## ECDF of proportion completed per cost type
temp <- dataAll %>%
        filter(Choice < 2) %>%
        mutate(Cost = factor(Cost, levels = list("Physical", "Cognitive", "Wait", "Easy"))) %>%
        group_by(SubjID, Cost) %>%
        summarise(Earnings = sum(Reward[Choice == 1] / 100),
                  pComplete = mean(Choice))

@@

grid.arrange(p1, p2, p3, ncol = 3)
```

@@

# matrix of coefficients
# 
temp <- lapply(mixLogis_main, function(model) {as.list(summary(model)$coefficients[2:4, 1])})
mixCoeffs <- as.matrix(bind_rows(temp)) #reduce(temp, full_join) 
dimnames(mixCoeffs) <- list(names(temp), substr(colnames(mixCoeffs), 5, 20))
mixCoeffs <- as.matrix(mixCoeffs[, match(rownames(mixCoeffs), colnames(mixCoeffs))])
mixCoeffs[is.na(mixCoeffs)] <- 1
mixCoeffs <- mixCoeffs[c("Cognitive", "Physical", "Wait", "Easy"), c("Cognitive", "Physical", "Wait", "Easy")]

@@

``` {r 16.2.3. Mixed Effects Model plot group coefficients, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}
# plot coefficient matrix (show pvals!)
corrplot(abs(mixLogis_mainBetas), 
         p.mat = mixLogis_mainPvals, 
         is.corr = F, 
         method = "color", 
         tl.col = "black", 
         tl.srt = 0, 
         insig = "p-value", 
         sig.level = -1, 
         type = "lower",
         cl.length = 3)
mtext("Comparison", side = 2, line = 1.5, cex = 1.5)
mtext("Reference Group", side = 3, line = 1, cex = 1.5, at = 2.5)

@@

This plot shows the AIC for every model. The figure below shows AIC and BIC for all the models. As predicted, the model with all main effects reduced the deviance the most ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2`).

@@

# separate by cost type and compute a linear model to predict half 2 from 1
sep <- temp %>% plyr::dlply("Cost", identity)
prepost$LM <- lapply(sep, function(data) {lm(data$Half_2 ~ data$Half_1)})

# get the coefficients and confidence intervals
# and concatenate
prepost$summary <- as.data.frame(cbind(t(sapply(prepost$LM, coefficients)), t(sapply(prepost$LM, confint))))
colnames(summary_prepost) <- c("Intercept", "Coefficient", "Int_CI-low", "Int_CI-high", "Beta_CI-low", "Beta_CI-high")
```

@@

``` {r 16.3.2. Plot Pre/Post, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}
prepost$plot <- dataAll %>%
                filter(Choice < 2) %>%
                group_by(SubjID, Cost) %>%
                summarise(propAccept_1 = mean(Choice[Half=="Half_1"]),
                          propAccept_2 = mean(Choice[Half=="Half_2"])) %>%
                ggplot(aes(propAccept_1, propAccept_2, fill = Cost)) +
                geom_point(size = 3, pch = 21, color = "black") +
                scale_fill_manual(values = cols) +
                xlim(0,1) +
                ylim(0,1) +
                geom_abline(slope = 1, intercept = 0, lty = 2) +
                theme(panel.grid.major = element_blank(),
                    panel.grid.minor = element_blank(),
                    panel.background = element_blank(),
                    axis.line = element_line(colour = "black"),
                    text = element_text(size = 16)))
```

>>>>

``` {r 16.2.1. Overall Proportion/Earnings, fig.align = "center", fig.width = 8, fig.height = 4, echo = FALSE}  
## ECDF of proportion completed per cost type
temp <- dataAll %>%
        filter(Choice < 2) %>%
        mutate(Cost = factor(Cost, levels = list("Physical", "Cognitive", "Wait", "Easy"))) %>%
        group_by(SubjID, Cost) %>%
        summarise(Earnings = sum(Reward[Choice == 1] / 100),
                  pComplete = mean(Choice))

@@

grid.arrange(p2, p3, ncol = 2)
```

@@

# matrix of coefficients
# 
temp <- lapply(mixLogis_main, function(model) {as.list(summary(model)$coefficients[2:4, 1])})
mixCoeffs <- as.matrix(bind_rows(temp)) #reduce(temp, full_join) 
dimnames(mixCoeffs) <- list(names(temp), substr(colnames(mixCoeffs), 5, 20))
mixCoeffs <- as.matrix(mixCoeffs[, match(rownames(mixCoeffs), colnames(mixCoeffs))])
mixCoeffs[is.na(mixCoeffs)] <- 0
mixCoeffs <- mixCoeffs[c("Cognitive", "Physical", "Wait", "Easy"), c("Cognitive", "Physical", "Wait", "Easy")]

@@

@@

This plot shows the AIC for every model. The figure below shows AIC and BIC for all the models. As predicted, the model with all main effects reduced the deviance the most ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2)`).

@@

# separate by cost type and compute a linear model to predict half 2 from 1
sep <- temp %>% plyr::dlply("Cost", identity)
prepost <- list()
prepost$LM <- lapply(sep, function(data) {lm(data$Half_2 ~ data$Half_1)})

# get the coefficients and confidence intervals
# and concatenate
prepost$summary <- as.data.frame(cbind(t(sapply(prepost$LM, coefficients)), t(sapply(prepost$LM, confint))))
colnames(prepost$summary) <- c("Intercept", "Coefficient", "Int_CI-low", "Int_CI-high", "Beta_CI-low", "Beta_CI-high")
```

@@

``` {r 16.3.2. Plot Pre/Post, echo=FALSE, fig.align = "center", fig.width = 6, fig.height = 5}
(prepost$plot <- dataAll %>%
                filter(Choice < 2) %>%
                group_by(SubjID, Cost) %>%
                summarise(propAccept_1 = mean(Choice[Half=="Half_1"]),
                          propAccept_2 = mean(Choice[Half=="Half_2"])) %>%
                ggplot(aes(propAccept_1, propAccept_2, fill = Cost)) +
                geom_point(size = 3, pch = 21, color = "black") +
                scale_fill_manual(values = cols) +
                xlim(0,1) +
                ylim(0,1) +
                geom_abline(slope = 1, intercept = 0, lty = 2) +
                theme(panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.background = element_blank(),
                      axis.line = element_line(colour = "black"),
                      text = element_text(size = 16)))
```
